\documentclass{article}

\include{assets/preamble}
\begin{document}

\begin{center}
  \Large\color{black!80}\textsc{Exercise 1}
\end{center}

Let's try use some of the things we learnt in the last section. If you
get stuck at any point put your hand up and I'll come over to help.\\

Create a folder titled \texttt{sage\_latex} on your computer. Download
\href{https://jwalton.info/assets/teaching/latex/scarlet.tex}{\emph{this file}} 
and save it in the folder which you just created.

\begin{enumerate}[label=\color{purple}\theenumi.]

  \item Check that you can compile the file you just downloaded
    (\texttt{scarlet.tex}).

  \item Extract the preamble from \texttt{scarlet.tex} and save it in its own
    separate file. You should name this separate file
    \texttt{preamble.tex}.

  \item Use the \texttt{\tb include} command to insert
    \texttt{preamble.tex} into \texttt{scarlet.tex}. Ensure that you can
    still compile \texttt{scarlet.tex}.

  \item{Create a new folder called \texttt{parts}. Extract the parts from 
    \texttt{scarlet.tex} and put them in their own separate files within
    the \texttt{parts} folder. Your folder structure should now look
    like the following:
    \vspace{0.25cm}
    \dirtree{%
    .1 \hspace{-1cm} sage\_latex/. 
    .2 scarlet.tex. 
      .2 parts/. 
      .3 part\_1.tex. 
      .3 part\_2.tex. 
      .2 preamble.tex. 
    }
    Ensure that you can still compile \texttt{scarlet.tex} with this new 
    folder structure.}

  \item Create a folder \texttt{fig/} within \texttt{sage\_latex/}. Download a
    detective-related image (think pipes, magnifying glasses etc.) and
    save it in the new \texttt{fig/} folder.

  \item Add the \texttt{fig/} folder to \texttt{graphicx}'s
    \texttt{graphicspath}.

  \item Include your detective image on the book cover. Your call to
    \texttt{\tb includegraphics} should \emph{not} reference the
    \texttt{fig/} folder.
    
  \item If you get this far try setting up your own thesis template.
    If you're in the School of Maths, Stats \& Physics consider using 
    \href{https://wiki.mas.ncl.ac.uk/mas/ThesisTemplate?highlight=\%28masthesis\%29}%
    {\emph{the thesis template provided on the wiki}}.
    Alternatively, take a look at other templates online; I'd also recommend having a
    look at the \href{https://ctan.org/pkg/classicthesis?lang=en}%
    {\emph{classic thesis template}}.

\end{enumerate}

\end{document}
